Legends for supplementary material

### 2019-04-28 Manuscript/Supplementary/supplementary_legends.Rmd
cleaning up legends

**Supplementary Figure 2. Clustered correlogram for genomic annotations at the 10 kb resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

@@

**Supplementary Figure 9. Clustered correlogram for genomic annotations at the 100 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

@@

<!--
**Supplementary Table 5. Data Summaries and Imbalance Ratios.** The total number of genomic bins included in the complete, training, and testing sets, as well as the subsequent imbalance ratios across resolutions and cell lines. Imbalance ratio is defined as the ratio of genomic bins that overlapped a flanked TAD boundary (minority class), divided by the number of genomic bins that did not overlap a flanked TAD boundary (majority class).
-->

<!--
**Supplementary Figure 2. Correlations between genomic annotations across cell lines and resolutions.** Upper and lower correlation heatmaps between genomic annotations for the GM12878 (A-D) and K562 (E-H) cell lines, across the 10 kb, 25 kb, 50 kb, and 100 kb resolutions (A, B, C, D; and E, F, G, H respectively). The correlations were evaluated on the total number of overlapped bases between flanked TAD boundaries and genomic annotations. High correlations (red) denote annotations that tended to occur colocally near TAD boundaries. Low correlations (blue) denote annotations that did not tend to occur near TAD boundaries together.

**Supplementary Figure 2A. Correlograms separated by genomic annotation category for overlap count predictor types, using 10 kb resolution data, on the GM12878 cell line** 
-->

<!--
**Supplementary Figrue 12. Barplots comparing model performance for each predictor type across 25 kb, 50 kb, and 100 kb data resolutions** Model performances were evaluated using F1-scores, MCCs, and balanced accuracies for each of the 4 resampling techniques, across both the GM12878 (A-C) and K562 (D-F) cell lines. Missing bars indicate that the model was unable to correctly predict any genomic regions that overlapped with flanked TAD boundaries in the test data, resulting in zero true positives. Bars that appear in the opposite direction (for MCC) indicate a negative correlation between the observed and predicted binary classifications of flanked TAD boundaries.

**Supplementary Figure 13. Line plots comparing models using the remaining resampling techniques with distance-type predictors.** Model performances were evaluated using F1-score, MCC, and balanced accuracy for each of the 4 data resolutions, across both the GM12878 (red, solid line) and K562 (blue; dashed line) cell lines. For a given metric, each point represents a model applied to a particular resolution with distance type predictors for the feature space, after which a particular resampling technique was used to create balanced classes on the trianing set, including none (A), random over-sampling (B), and random under-sampling (C).

**Supplementary Figure 14A. Variable importance of the top 20 most predictive genomic annotations for models using no resampling technique with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model with distance-type predictors at the 10 kb data resolution, while not performing a class balancing technique, for each cell line respectively.

**Supplementary Figure 14B. Variable importance of the top 20 most predictive genomic annotations for models using random over-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random over-sampling to create balanced classes, for each cell line respectively.

**Supplementary Figure 14C. Variable importance of the top 20 most predictive genomic annotations for models using random under-sampling with distance-type predictors.** The list of genomic features are the union of the top 20 most important genomic annotations across resolutions for the GM12878 (A) and K562 (B) cell lines. Variable importance is assigned on a continuous scale (range: 0-100). Grid entries filled in gray denote an annotation that was not featured as one of the top 20 most predictive variables in a given model. The genomic annotations are sorted by highest level of importance obtained from a random forest model using distance-type predictors at the 10 kb data resolution, while using random under-sampling to create balanced classes, for each cell line respectively.
-->

<!--
**Supplementary Figures 9-23. Precision-Recall curves for 25 kb, 50kb, and 100kb data.** Precision-recall curves were used to initially compare performance of random forest models with different predictor types on 25 kb, 50kb, and 100kb resolution data, across each resampling technique. GM12878 (solid line) and K562 (dashed line) cell lines were compared with predictor type-specific models which included overlap counts (blue), overlap percents (purple), log distance (green), and all three combined (red). 
-->

<!--
**Supplementary Table 2. Area under Precision-Recall Curves.** Comparison of models applied to different data resolutions, resampling techniques, and predictor types for each of the two cell lines in terms of AUPRC. The column labeled "All" denotes models with all 3 combined predictor types.
-->

<!--
**Figure 3. Recursive Feature Elimination for 25 kb, 50 kb, and 100 kb data** Beginning with the full set of distance type predictors for each cell line, models built on 25 kb, 50 kb, and 100 kb resolution data were recursively evaluated at different subsets of feature size. For convenience and computational efficiency, feature size decreasing in powers of 2 was considered. The maximum size for feature subsets differed between cell line due the available annotations that were considered and provided in Supplementary Table 1. Near optimal performance was achieved using the top 32 distance type predictors for both the GM12878 (red) and K562 cell lines (blue).
-->

>>>>

<!--
**Supplementary Figure 2. Clustered correlogram for genomic annotations at the 10 kb resolution for the GM12878 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.

@@

**Supplementary Figure 9. Clustered correlogram for genomic annotations at the 100 kb resolution for the K562 cell line.** Pairwise correlations between the total number of instances where regions defined by genomic annotations overlapped with flanked TAD boundaries on the linear genome. Positive correlations are denoted in red, while negative correlations are denoted in blue. The upper triangular matrix of correlations was clustered using Ward's method. Delineated regions of high correlations indicate genomic annotations that are colocalized at TAD boundaries.
-->

**Supplementary Table 9. Imbalance ratios.** The mean (SD) imbalance ratios across the autosomal chromosomes for each resolution and cell line. Imbalance ratios are defined as the ratio of minority classes to majority classes are provided across resolution and cell line. The minority class is the set of genomic bins that overlap with flanked TAD boundaries, while the majority class is the set of genomic bins that do not overlap with any flanked TAD boundary.

**Supplementary Figure 16. Imbalance ratios vs resolution.** Scatter plots illustrating the relationship between imbalance ratios and resolutions, for each cell line.

@@
